WIDS 2024 Final Project

### 2024-01-12 Code/Full R Code.qmd
worked on paper

From the summary, we can see the demographics has most of its variables skewed. This will be examined in closer detail in the exploratory data analysis. only two columns have NA values and each of those columns NA values represent less than 10% of the data. There is not an immediate cause to take action on these NA values, although they will be examined in greater detail in the EDA.

@@

#### 2.4.2.1 Graph of regression estimate by decade and year

>>>>

From the summary, we can see the demographics has most of its variables skewed. This will be examined in closer detail in the exploratory data analysis. Only two columns have NA values and each of those columns NA values represent less than 10% of the data. There is not an immediate cause to take action on these NA values, although they will be examined in greater detail in the EDA.

@@

#### 2.4.2.1 Graph of regression estimate by decade and region
